---
title: "Past Pandemics City Zuerich"
author: "Katarina Matthes"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    code_folding: show
    self_contained: true
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

The orange area is the period of World War 1, the grey areas are the periods of pandemics, the red dashed lines represent breakpoints and the dotted lines the corresponding 95% CI.

# Data 1910-1925
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, warning=FALSE, fig.height =15 , fig.width = 15,message=FALSE}
function_plot_zurich()
```


Births per marriage were calculated with the number of births 39 weeks after the marriage. Am not quite sure if this makes sense. But a direct comparison makes even less sense to me. Because first fewer marriages and then fewer births (9 months later at the earliest).

```{r, echo=FALSE, warning=FALSE, fig.height =18 , fig.width = 18,message=FALSE}
function_plot_birth()
```

# Data Swiss-re 1918-1930
The absence is displayed in relation to the number of working days. Absence because of other reasons = Absence total - Illness.
<br />
<br />
The peaks in "absences for other reasons" reflect the August vacation season. "Absences for other reasons" in August 1918 high for women, as in the following years. For men, highest in July, but also increased the months before -> reason: military absence. But why highest in July?
<br />
<br />
From 1926, seasonal absenteeism increases in summer -> change in labor protection law? Absences due to illness also increase among women from 1926 onward. A high level of absenteeism among women can be seen particularly in the winter of 1927(Reasons? Since it is not that high for men).
<br />
<br />
In the influenza winter of 1928/1929, an increase in absences due to illness can be seen in both sexes. 

```{r, echo=FALSE, warning=FALSE, fig.height =18 , fig.width = 18,message=FALSE}
function_plot_swiss_re()
```

# Time Series Analysis


## Marriages
The number of marriages per 100'000 inhabitans goes down directly after the beginning of the 1st World War and up again after the end in 1919. The number increases even further than before the 1st World War.

```{r, echo=FALSE, warning=FALSE, fig.height =10 , fig.width = 10,message=FALSE}
function_ts_marriage()
```

## Birth
The birth rate per 100'000 inhabitants goes down exactly 38 weeks after the decline in marriages! And 25 weeks after the marriages go up again. But the birth rate is not rising as high as before the 1st World War.

```{r, echo=FALSE, warning=FALSE, fig.height =10 , fig.width = 10,message=FALSE}
function_ts_birth()
```

## Birth per Marriage
The number of births per marriages decreased.

```{r, echo=FALSE, warning=FALSE, fig.height =10 , fig.width = 10,message=FALSE}
function_ts_marriage_birth()
```

## Stillborn

```{r, echo=FALSE, warning=FALSE, fig.height =10 , fig.width = 10,message=FALSE}
function_ts_stillborn()
```
